Table

### 2021-02-22 table.Rmd
edits: Rmd output directory
edits: delete backslash

---
title: "Table"
output:
  pdf_document: default
---

@@

source(here::here("/empirical/analysis_lm_bf.R"))

>>>>

---
title: "Table"
output:
  pdf_document: default
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---

@@

source(here::here("empirical/analysis_lm_bf.R"))
